An Open Repository of Real-Time COVID-19 Indicators

### 2021-10-03 indicators/paper/paper.tex
Tweak last paragraph in Sect 1A

Altogether, we collect over 170 signals from 12 distinct sources, aggregate and
process them, and provide them in a common format for public access. This
unifies both unique (not available anywhere else) and standard COVID data
streams into a single common format, enabling efficient comparison and modeling.
A summary of the data sources and signals in the API is in
Table~\ref{tab:sources_signals}, and detailed documentation is available at
\url{https://cmu-delphi.github.io/delphi-epidata/api/covidcast_signals.html}.

>>>>

Altogether, we produce over 170 signals from 12 distinct sources, and provide
them in a common format for public access. This unifies both unique (unavailable
anywhere else) and standard COVID data streams into a single common 
format, enabling efficient comparison and modeling. A summary of the data
sources and signals in the API is in Table~\ref{tab:sources_signals}, and
detailed documentation is available online at
\url{https://cmu-delphi.github.io/delphi-epidata/api/covidcast_signals.html}.
